What would the world be like without the normal curve?
========================================================

Once upon a time there was a land called Praxis. Mr and Mrs Boxy lived there happily in 01 Uniform, Distribution. 

They were content in this land. They made many babies. Here is a family portrait.
```{r, echo=FALSE}
library(ggplot2)

x <- runif(1000)
qplot(x) + ggtitle("Uniform Babies")
```

They often took their children to hike the uneven peaks of Gammamountain.
```{r, echo=FALSE}
qplot(rgamma(1000, 3, 4)) + ggtitle("Gammamountain")
```

Little did they know that the Gammamountains are the home of the February 29th movement; a revolutionary rebel group led by General Zod fighting the kleptocratic loyalist government.  As a defensive measure against loyalist forces, General Zod has deployed a series of spike traps.  These spike traps are aptly named "Dirac Delta Deathtraps":
```{r, echo=FALSE}
x = seq(-5, 5, by = 0.05)
y = rep(1, length(x))
plot(x,y,type="h",xlim=c(-0.6,0.6),ylim=c(0,2))
```